### 2017-09-03 doc/chap-3-refman.tex
1. Added a two-step heap abstraction (global/local) for optimization. 2. Removed Concrete Abstraction (implementation of the Singleton Abstraction) 3. Upgraded the console debugger. 4. Added simple modeling: window.navigator and RegExp.prototype.test 5. Added README files for the third-party liceses thanks to Alexander Jordan. 6. Added a list of ignored tests when JS modeling is not used.

\medskip
The \verb!astRewrite! command parses the JavaScript code in a given file and
rewrites its AST representation into a simpler AST.
The \verb!astRewriter! phase performs three kinds of AST transformations:
\begin{itemize}
\item \verb!Hoister! lifts the declarations of functions and variables inside
programs and functions up to the beginning of them.
\item \verb!Disambiguator! checks some static restrictions and renames identifiers
to unique names.
\item \verb!WithRewriter! rewrites the \verb!with! statements that do not include
any dynamic code generation such as \verb!eval! into other statements without using
the \verb!with! statement but with the same semantics.
\end{itemize}

@@

The \verb!help! command displays a list of available commands and
the \verb!help <command>! command displays the usage of the \verb!<command>!.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > help print
usage: print state(-all) ({keyword})
       print block
       print loc {LocName} ({keyword})
       print func {functionID}
       print worklist
       print ipsucc
       print trace
       print cfg
\end{verbatim}
}
\noindent
shows the usage of the \verb!print! command.

@@

\medskip\noindent
\fbox{\texttt{print block}}\\[.2em]
The \verb!print block! command displays the information of
a given block.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
Iter[1] > print block
Block[0] -> [1], ExitExc
  [0] noop(StartOfFile)
  [1] <>Global<>ignore1 := alloc() @ #1
  [2] obj := <>Global<>ignore1
  [3] <>obj<>1 := <>Global<>toObject(obj) @ #2
  [4] <>obj<>2 := <>Global<>toObject(Array) @ #3
  [5] <>obj<>3 :=
      <>Global<>toObject(<>obj<>2["prototype"]) @ #4
  [6] <>obj<>1["pop"] := <>obj<>3["pop"]
  [7] <>obj<>4 := <>Global<>toObject(obj) @ #5
  [8] <>obj<>4[4294967294] := "x"
  [9] <>obj<>5 := <>Global<>toObject(obj) @ #6
  [10] <>obj<>5["length"] := - 1
  [11] <>obj<>6 := <>Global<>toObject(obj) @ #7
  [12] <>arguments<>7 := allocArg(0) @ #8
  [13] <>fun<>8 :=
       <>Global<>toObject(<>obj<>6["pop"]) @ #9
\end{verbatim}
}

>>>>

\medskip
The \verb!astRewrite! command parses the JavaScript code in a given file and
rewrites its AST representation into a simpler AST.
The \verb!astRewriter! phase performs three kinds of AST transformations:
\begin{itemize}
\item \verb!Hoister! lifts the declarations of functions and variables inside
programs and functions up to the beginning of them.
\item \verb!Disambiguator! checks some static restrictions and renames identifiers
to unique names.
\item \verb!WithRewriter! rewrites the \verb!with! statements that do not include
any dynamic code generation such as \verb!eval! into other statements without using
the \verb!with! statement but with the same semantics~\cite{dls13,withtr}.
\end{itemize}

@@

The \verb!help! command displays a list of available commands and
the \verb!help <command>! command displays the usage of the \verb!<command>!.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > help print
usage: print state(-all) ({keyword})
       print block ({fid}:{bid})
       print loc {LocName} ({keyword})
       print func {functionID}
       print worklist
       print ipsucc
       print trace
       print cfg
\end{verbatim}
}
\noindent
shows the usage of the \verb!print! command.

@@

\medskip\noindent
\fbox{\texttt{print block ({}{})}}\\[.2em]
\fbox{\texttt{print block (\{fid\}\{bid\})}}\\[.2em]
The \verb!print block! command displays the information of
the current block. For example:
{\small
\begin{verbatim}
<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
Iter[1] > print block
Block[0] -> [1], ExitExc
  [0] noop(StartOfFile)
  [1] <>Global<>ignore1 := alloc() @ #1
  [2] obj := <>Global<>ignore1
  [3] <>obj<>1 := <>Global<>toObject(obj) @ #2
  [4] <>obj<>2 := <>Global<>toObject(Array) @ #3
  [5] <>obj<>3 :=
      <>Global<>toObject(<>obj<>2["prototype"]) @ #4
  [6] <>obj<>1["pop"] := <>obj<>3["pop"]
  [7] <>obj<>4 := <>Global<>toObject(obj) @ #5
  [8] <>obj<>4[4294967294] := "x"
  [9] <>obj<>5 := <>Global<>toObject(obj) @ #6
  [10] <>obj<>5["length"] := - 1
  [11] <>obj<>6 := <>Global<>toObject(obj) @ #7
  [12] <>arguments<>7 := allocArg(0) @ #8
  [13] <>fun<>8 :=
       <>Global<>toObject(<>obj<>6["pop"]) @ #9
\end{verbatim}
}

Moreover, it displays the information of the given block denoted
by the id of a function, the id of a block, and the kind of the block.
For example:

{\small
\begin{verbatim}
<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
Iter[1] > print block 0:4
Block[4] -> Exit, ExitExc
  [0] shift := <>Global<>ignore6
  [1] __result1 := shift !== "x"
  [2] __expect1 := false
  [3] <>obj<>10 := <>Global<>toObject(obj) @ #13
  [4] __result2 := <>obj<>10["length"] !== 1
  [5] __expect2 := false
  [6] <>obj<>11 := <>Global<>toObject(obj) @ #14
  [7] __result3 := <>obj<>11[0] !== "y"
  [8] __expect3 := false
  [9] <>obj<>12 := <>Global<>toObject(obj) @ #15
  [10] __result4 := <>obj<>12[1] !== undefined
  [11] __expect4 := false
  [12] noop(EndOfFile)
\end{verbatim}
}
